Ground state energy of quantum dots using the coupled cluster method

### 2018-06-06 project_2/article/article.tex
Table templates
Table column headers
Add results for N = 12 particles
Table for N=2, missing 11 and 12 shells

>>>>

\section{Results}

    \begin{table}
        \centering
        \caption{N = 2}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\ \hline
                         &  1  & 0.596333 & 0.596333 & 0.596333 \\
                         &  2  & 0.596333 & 0.512520 & 0.512520 \\
                         &  3  & 0.526903 & 0.505972 & 0.442235 \\
                         &  4  & 0.526903 & 0.499216 & 0.442011 \\
                     0.1 &  5  & 0.525666 & 0.497172 & 0.443293 \\
                         &  6  & 0.525666 & 0.494232 & 0.443145 \\
                         &  7  & 0.525635 & 0.493142 & 0.443056 \\
                         &  8  & 0.525635 & 0.491895 & 0.442981 \\
                         &  9  & 0.525635 & 0.491262 & 0.491262 \\
                         &  10 & 0.525635 & 0.490649 & 0.442886 \\
                         &  11 & & & \\
                         &  12 &  & & \\ \hline

                         &  1  & 1.886227 & 1.886227 & 1.886227 \\
                         &  2  & 1.886227 & 1.786914 & 1.786914 \\
                         &  3  & 1.799856 & 1.778903 & 1.681979 \\
                         &  4  & 1.799856 & 1.760117 & 1.673881 \\
                     0.5 &  5  & 1.799748 & 1.754385 & 1.670053 \\
                         &  6  & 1.799748 & 1.748232 & 1.667804 \\
                         &  7  & 1.799745 & 1.745231 & 1.666474 \\
                         &  8  & 1.799745 & 1.742548 & 1.665494 \\
                         &  9  & 1.799743 & 1.740860 & 1.6648053 \\
                         &  10 & 1.799743 & 1.739444 & 1.664270 \\
                         &  11 & & & \\
                         &  12 &  & & \\ \hline

                         &  1  & 3.253314 & 3.253314 & 3.253314 \\
                         &  2  & 3.253314 & 3.152328 & 3.152328 \\
                         &  3  & 3.162691 & 3.141827 & 3.039048 \\
                         &  4  & 3.162691 & 3.118679 & 3.025273 \\
                     1.0 &  5  & 3.161921 & 3.110967 & 3.017944 \\
                         &  6  & 3.161921 & 3.103338 & 3.013923 \\
                         &  7  & 3.161909 & 3.099324 & 3.011405 \\
                         &  8  & 3.161909 & 3.095916 & 3.009621 \\
                         &  9  & 3.161909 & 3.093662 & 3.008343 \\
                         &  10 & 3.161909 & 3.091818 & 3.007357 \\
                         &  11 & & & \\
                         &  12 &  & & \\ \hline

                         &  1  & 5.772454 & 5.772454 & 5.772454 \\
                         &  2  & 5.772454 & 5.671234 & 5.671234 \\
                         &  3  & 5.679048 & 5.658272 & 5.553528 \\
                         &  4  & 5.679048 & 5.631669 & 5.534333 \\
                     2.0 &  5  & 5.677282 & 5.622092 & 5.523490 \\
                         &  6  & 5.677282 & 5.613118 & 5.517552 \\
                         &  7  & 5.677206 & 5.608130 & 5.513709 \\
                         &  8  & 5.677206 & 5.604026 & 5.511012 \\
                         &  9  & 5.677204 & 5.601216 & 5.509050 \\
                         &  10 & 5.677204 & 5.598946 & 5.507540 \\
                         &  11 &  & & \\
                         &  12 &  & & \\
            \end{tabular}
        \end{ruledtabular}
        \label{tab:N2}        
    \end{table}

    \begin{table}
        \centering
        \caption{N = 6}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF)

            \end{tabular}
        \end{ruledtabular}
        \label{tab:N6}        
    \end{table}

    \begin{table}
        \centering
        \caption{N = 12}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF)

            \end{tabular}
        \end{ruledtabular}
        \label{tab:N12}        
    \end{table}

    \begin{table}
        \centering
        \caption{N = 20}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF)

            \end{tabular}
        \end{ruledtabular}
        \label{tab:N20}        
    \end{table}
